---
output:
  pdf_document: default
  html_document: default
---
# Final Report
### by Analyst
### `r Sys.Date()`

**Part 1 Standard Data**

```{r library, include=FALSE}
library(ggplot2)
library(kableExtra)
library(tinytex)

```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r echo=FALSE, warning=FALSE}
stddata_HDL <- dplyr::filter(standard_data(), grepl("HDL", std_id))
  
linearMod_HDL <- lm(result ~ expected_raw, data = stddata_HDL)
```

Summary of the linear regression model for analyte *HDL*
```{r echo=FALSE}
summary(linearMod_HDL)
```


```{r echo=FALSE}
b_HDL   <- coef(linearMod_HDL)
```


```{r echo=FALSE}
ggplot(data = stddata_HDL, 
                 aes(stddata_HDL$expected_raw, stddata_HDL$result)) + 
            geom_point() + 
            labs(title = "Standard plot of Analyte HDL",
                 x = "Expected raw data of Analyte HDL",
                 y = "Final result of Analyte HDL")
```

```{r echo=FALSE}
stddata_LDL <- dplyr::filter(standard_data(), grepl("LDL", std_id))
  
linearMod_LDL <- lm(result ~ expected_raw, data = stddata_LDL)
```

Summary of the linear regression model for analyte *LDL*
```{r echo=FALSE}
summary(linearMod_LDL)
```

```{r echo=FALSE}
b_LDL   <- coef(linearMod_LDL)
```


```{r echo=FALSE}
ggplot(data = stddata_LDL, 
                 aes(stddata_LDL$expected_raw, stddata_LDL$result)) + 
            geom_point() + 
            labs(title = "Standard plot of Analyte LDL",
                 x = "Expected raw data of Analyte LDL",
                 y = "Final result of Analyte LDL")
```

```{r echo=FALSE}
stddata_Triglycerides <- dplyr::filter(standard_data(), grepl("Triglycerides", std_id))
  
linearMod_Triglycerides <- lm(result ~ expected_raw, data = stddata_Triglycerides)
```

Summary of the linear regression model for analyte *Triglycerides*
```{r echo=FALSE}
summary(linearMod_Triglycerides)
```

```{r echo=FALSE}
b_Triglycerides   <- coef(linearMod_Triglycerides)
```


```{r echo=FALSE}
ggplot(data = stddata_Triglycerides, 
                 aes(stddata_Triglycerides$expected_raw, stddata_Triglycerides$result)) + 
            geom_point() + 
            labs(title = "Standard plot of Analyte Triglycerides",
                 x = "Expected raw data of Analyte Triglycerides",
                 y = "Final result of Analyte Triglycerides")
```

**Part 2 Final Results**

The predicted results are shown in the following figures:

```{r echo=FALSE}
analyst_result_HDL <- dplyr::filter(analyst_analysis_result(), grepl("HDL", analyte_name))

ggplot(data = analyst_result_HDL, 
                 aes(as.numeric(analyst_result_HDL$expected_raw),
                     as.numeric(analyst_result_HDL$result))) + 
            geom_point() + 
            labs(title = "Predicted Results plot of Analyte HDL",
                 x = "Expected raw data of Analyte HDL",
                 y = "Final result of Analyte HDL")
```

```{r echo=FALSE}
analyst_result_LDL <- dplyr::filter(analyst_analysis_result(), grepl("LDL", analyte_name))

ggplot(data = analyst_result_LDL, 
                 aes(as.numeric(analyst_result_LDL$expected_raw),
                     as.numeric(analyst_result_LDL$result))) + 
            geom_point() + 
            labs(title = "Predicted Results plot of Analyte LDL",
                 x = "Expected raw data of Analyte LDL",
                 y = "Final result of Analyte LDL")
```


```{r echo=FALSE}
analyst_result_Triglycerides <- dplyr::filter(analyst_analysis_result(), grepl("Triglycerides", analyte_name))

ggplot(data = analyst_result_Triglycerides, 
                 aes(as.numeric(analyst_result_Triglycerides$expected_raw),
                     as.numeric(analyst_result_Triglycerides$result))) + 
            geom_point() + 
            labs(title = "Predicted Results plot of Analyte Triglycerides",
                 x = "Expected raw data of Analyte Triglycerides",
                 y = "Final result of Analyte Triglycerides")
```

The predicted results are shown in the following table:

```{r echo=FALSE}
library(knitr)
kable(analyst_analysis_result(), caption = "Predicted results table")
```
